---
header-includes:
- \usepackage{amssymb, amsmath, amsthm}
- \usepackage{tabu}
- \newcommand{\E}{\mathbb{E}}
- \newcommand{\var}{{\rm Var}}
- \newcommand{\N}{\mathcal{N}}
output: pdf_document
---

\noindent \begin{tabu} to \textwidth {@{}X[4 l] @{}X[r]}
  \textbf{Project 6}           & \\ 
  \textbf{MFE 405: Computational Finance}   & \\ 
  \textbf{Professor Goukasian}         & \\
  \textbf{Students: Xiahao Wang}
\end{tabu}

## This is a summary of the project for data visualisation, for detail implementation and result,
## please refer to the print out of the program

## Qn 1.Fixed Strike Lookback Call and Put

Implementation in C++ code

```{r}
callPrice <- c(8.78015,11.9791,15.8853,18.6341,
               21.8975,24.6296,28.9913,32.5146,34.2307,40.4474)
volatility <- seq(12,48,4)
plot(y=callPrice,x=volatility, xlab="Volatility",
     ylab="Call Price", main="Call Price", type="l")

putPrice <- c(9.26799,11.9689,14.734,16.77,19.181,
              22.5869,23.7869,26.3841,
              29.9664,31.7712)
plot(y=putPrice,x=volatility, xlab="Volatility",
     ylab="Put Price", main="Put Price", type="l")
```


## Qn 2 jump-diffusion process

(a) Option Price with different Lamda one and two over the years

```{r}
fixedLambdaOne <- read.csv("~/Documents/ucla/Dropbox/Quarter2/Computational Finance/HW/ComputationalFinanceProject6/Data/lamdaOne_0.2.csv", header=TRUE,sep = ",")

fixedLambdaTwo <- read.csv("~/Documents/ucla/Dropbox/Quarter2/Computational Finance/HW/ComputationalFinanceProject6/Data/lamdaTwo_0.4.csv", header=TRUE,sep = ",")

lamdatwo <- seq(0,0.8,0.1)
year <- seq(3,8,1)
color1 <- c("black","blue","green","yellow","pink","red","orange","purple","grey","tomato")
color2 <- c("black","blue","green","yellow","pink","red","orange","purple")

plot(x= year, y= fixedLambdaOne[fixedLambdaOne$lamdaTwo==0,]$Option_Price, type = "l",ylim = c(200,6000), ylab = "Default Option Price", main = "LamdaOne = 0.2, Option Price varies with LamdaTwo")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.1,]$Option_Price, type="l",col="blue")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.2,]$Option_Price, type="l",col="green")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.3,]$Option_Price, type="l",col="yellow")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.4,]$Option_Price, type="l",col="pink")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.5,]$Option_Price, type="l",col="red")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.5,]$Option_Price, type="l",col="orange")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.6,]$Option_Price, type="l",col="purple")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.7,]$Option_Price, type="l",col="grey")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.8,]$Option_Price, type="l",col="tomato")
legend("bottomright", c("0", "0.1","0.2","0.3","0.4","0.5","0.6","0.7","0.8"), col=color1, lwd=5,cex=0.5)

plot(x= year, y= fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.05,]$Option_Price, type = "l",ylim = c(200,7000), ylab = "Default Option Price", main = "LamdaTwo = 0.4, Option Price varies with LamdaOne")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.1,]$Option_Price, type="l",col="blue")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.15,]$Option_Price, type="l",col="green")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.2,]$Option_Price, type="l",col="yellow")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.25,]$Option_Price, type="l",col="pink")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.30,]$Option_Price, type="l",col="red")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.35,]$Option_Price, type="l",col="orange")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.40,]$Option_Price, type="l",col="purple")
legend("bottomright", c("0.05", "0.1","0.15","0.2","0.25","0.3","0.35","0.4"), col=color2, lwd=5,cex=0.5)





```

(b) Probability with different Lamda one and two over the years
```{r}
plot(x= year, y= fixedLambdaOne[fixedLambdaOne$lamdaTwo==0,]$Probability, type = "l",ylim = c(0,1), ylab = "Default Probability", main = "LamdaOne = 0.2, Option Price varies with LamdaTwo")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.1,]$Probability, type="l",col="blue")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.2,]$Probability, type="l",col="green")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.3,]$Probability, type="l",col="yellow")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.4,]$Probability, type="l",col="pink")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.5,]$Probability, type="l",col="red")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.5,]$Probability, type="l",col="orange")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.6,]$Probability, type="l",col="purple")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.7,]$Probability, type="l",col="grey")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.8,]$Probability, type="l",col="tomato")
legend("bottomright", c("0", "0.1","0.2","0.3","0.4","0.5","0.6","0.7","0.8"), col=color1, lwd=5,cex=0.5)

plot(x= year, y= fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.05,]$Probability, type = "l",ylim = c(0.5,1), ylab = "Default Probability", main = "LamdaTwo = 0.4, Option Price varies with LamdaOne")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.1,]$Probability, type="l",col="blue")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.15,]$Probability, type="l",col="green")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.2,]$Probability, type="l",col="yellow")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.25,]$Probability, type="l",col="pink")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.30,]$Probability, type="l",col="red")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.35,]$Probability, type="l",col="orange")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.40,]$Probability, type="l",col="purple")
legend("bottomright", c("0.05", "0.1","0.15","0.2","0.25","0.3","0.35","0.4"), col=color2, lwd=5,cex=0.5)
```

(c) Probability with different Lamda one and two over the years
```{r}
plot(x= year, y= fixedLambdaOne[fixedLambdaOne$lamdaTwo==0,]$Expected_Tau, type = "l",ylim = c(0,8), ylab = "Expected_Tau", main = "LamdaOne = 0.2, Option Price varies with LamdaTwo")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.1,]$Expected_Tau, type="l",col="blue")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.2,]$Expected_Tau, type="l",col="green")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.3,]$Expected_Tau, type="l",col="yellow")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.4,]$Expected_Tau, type="l",col="pink")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.5,]$Expected_Tau, type="l",col="red")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.5,]$Expected_Tau, type="l",col="orange")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.6,]$Expected_Tau, type="l",col="purple")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.7,]$Expected_Tau, type="l",col="grey")
lines(x=year, y=fixedLambdaOne[fixedLambdaOne$lamdaTwo==0.8,]$Expected_Tau, type="l",col="tomato")
legend("bottomright", c("0", "0.1","0.2","0.3","0.4","0.5","0.6","0.7","0.8"), col=color1, lwd=5,cex=0.5)

plot(x= year, y= fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.05,]$Expected_Tau, type = "l",ylim = c(0,2.5), ylab = "Expected_Tau", main = "LamdaTwo = 0.4, Option Price varies with LamdaOne")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.1,]$Expected_Tau, type="l",col="blue")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.15,]$Expected_Tau, type="l",col="green")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.2,]$Expected_Tau, type="l",col="yellow")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.25,]$Expected_Tau, type="l",col="pink")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.30,]$Expected_Tau, type="l",col="red")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.35,]$Expected_Tau, type="l",col="orange")
lines(x=year, y=fixedLambdaTwo[fixedLambdaTwo$lamdaOne==0.40,]$Expected_Tau, type="l",col="purple")
legend("bottomright", c("0.05", "0.1","0.15","0.2","0.25","0.3","0.35","0.4"), col=color2, lwd=5,cex=0.5)
```
