---
header-includes:
- \usepackage{amssymb, amsmath, amsthm}
- \usepackage{tabu}
- \newcommand{\E}{\mathbb{E}}
- \newcommand{\var}{{\rm Var}}
- \newcommand{\N}{\mathcal{N}}
output: pdf_document
---

## Qn 2.
Explicit Finite-Difference method: 
$\sigma \sqrt(dx)$
```{r}
ds_05 <- read.csv("~/Documents/ucla/Dropbox/Quarter2/Computational Finance/HW/ComputationalFinanceProject7/Data/ds_05.csv", header=F,sep = ",")
ds_10 <- read.csv("~/Documents/ucla/Dropbox/Quarter2/Computational Finance/HW/ComputationalFinanceProject7/Data/ds_1.csv", header=F,sep = ",")
ds_125 <- read.csv("~/Documents/ucla/Dropbox/Quarter2/Computational Finance/HW/ComputationalFinanceProject7/Data/ds_125.csv", header=F,sep = ",")

priceRange <- seq(4,16,1)
colnames(ds_05) <- c("S","Method","type","OptionP")
colnames(ds_10) <- c("S","Method","type","OptionP")
colnames(ds_125) <- c("S","Method","type","OptionP")
color1 <- c("red","blue","yellow")
```
At S = $10

At ds = 0.25

Call:                      

EFD = $0.66231800
IFD = $0.661739000
CNFD = $0.662029000

Put:

EFD = $0.481483000
IFD = $0.480550000
CNFD = $0.481011000

At ds = 1

Call: 

EFD = $0.624669000
IFD = $0.623914000
CNFD = $0.624292000

Put:

EFD	= $0.440889000
IFD = $0.439993000
CNFD = $0.440441000

At ds = 1.25

Call:

EFD = $0.597990000
IFD = $0.597213000
CNFD = $0.59760200

Put:

EFD = $0.416292000
IFD = $0.415392000
CNFD = $0.41584200

European Vanilla Call is at 0.66 and Put at 0.46, hence we can observe that the apporximation becomes less accuraet when ds increases.


```{r}
# Call ds =0.25
EFD <- ds_05[ds_05$Method=="EFD",]
IFD <- ds_05[ds_05$Method=="IFD",]
CNFD <- ds_05[ds_05$Method=="CNFD",]

EFDCall <- EFD[EFD$type=="Call",]
IFDCall <- IFD[IFD$type=="Call",]
CNFDCall <- CNFD[CNFD$type=="Call",]

plot(x= priceRange, y= EFDCall$OptionP,type = "l",ylim = c(0,7), ylab = "Option Price", main = "dS = 0.5, Call Options", col="red")
lines(x=priceRange, y= IFDCall$OptionP, type="l",col="blue")
lines(x=priceRange, y= CNFDCall$OptionP, type="l",col="yellow")
legend("topleft", c("EFD","IFD","CNFD"), col=color1, lwd=5,cex=0.5)

# Put ds =0.5
EFDPut <- EFD[EFD$type=="Put",]
IFDPut <- IFD[IFD$type=="Put",]
CNFDPut <- CNFD[CNFD$type=="Put",]

plot(x= priceRange, y= EFDPut$OptionP,type = "l",ylim = c(0,7), ylab = "Option Price", main = "dS = 0.5, Put Options", col="red")
lines(x=priceRange, y= IFDPut$OptionP, type="l",col="blue")
lines(x=priceRange, y= CNFDPut$OptionP, type="l",col="yellow")
legend("topright", c("EFD","IFD","CNFD"), col=color1, lwd=5,cex=0.5)

# Call ds =1
EFD_10 <- ds_10[ds_10$Method=="EFD",]
IFD_10 <- ds_10[ds_10$Method=="IFD",]
CNFD_10 <- ds_10[ds_10$Method=="CNFD",]

EFDCall_10 <- EFD_10[EFD_10$type=="Call",]
IFDCall_10 <- IFD_10[IFD_10$type=="Call",]
CNFDCall_10 <- CNFD_10[CNFD_10$type=="Call",]

plot(x= priceRange, y= EFDCall_10$OptionP,type = "l",ylim = c(0,7), ylab = "Option Price", main = "dS = 1, Call Options", col="red")
lines(x=priceRange, y= IFDCall_10$OptionP, type="l",col="blue")
lines(x=priceRange, y= CNFDCall_10$OptionP, type="l",col="yellow")
legend("topleft", c("EFD","IFD","CNFD"), col=color1, lwd=5,cex=0.5)

# put ds =1
EFDPut_10 <- EFD_10[EFD_10$type=="Put",]
IFDPut_10 <- IFD_10[IFD_10$type=="Put",]
CNFDPut_10 <- CNFD_10[CNFD_10$type=="Put",]

plot(x= priceRange, y= EFDPut_10$OptionP,type = "l",ylim = c(0,7), ylab = "Option Price", main = "dS = 1, Put Options", col="red")
lines(x=priceRange, y= IFDPut_10$OptionP, type="l",col="blue")
lines(x=priceRange, y= CNFDPut_10$OptionP, type="l",col="yellow")
legend("topright", c("EFD","IFD","CNFD"), col=color1, lwd=5,cex=0.5)

# Call ds =1.25
EFD_125 <- ds_125[ds_125$Method=="EFD",]
IFD_125 <- ds_125[ds_125$Method=="IFD",]
CNFD_125 <- ds_125[ds_125$Method=="CNFD",]

EFDCall_125 <- EFD_125[EFD_125$type=="Call",]
IFDCall_125 <- IFD_125[IFD_125$type=="Call",]
CNFDCall_125 <- CNFD_125[CNFD_125$type=="Call",]

plot(x= priceRange, y= EFDCall_125$OptionP,type = "l",ylim = c(0,7), ylab = "Option Price", main = "dS = 1.25, Call Options", col="red")
lines(x=priceRange, y= EFDCall_125$OptionP, type="l",col="blue")
lines(x=priceRange, y= EFDCall_125$OptionP, type="l",col="yellow")
legend("topleft", c("EFD","IFD","CNFD"), col=color1, lwd=5,cex=0.5)


EFDPut_125 <- EFD_125[EFD_125$type=="Put",]
IFDPut_125 <- IFD_125[IFD_125$type=="Put",]
CNFDPut_125 <- CNFD_125[CNFD_125$type=="Put",]

plot(x= priceRange, y= EFDPut_125$OptionP,type = "l",ylim = c(0,7), ylab = "Option Price", main = "dS = 1.25, Put Options", col="red")
lines(x=priceRange, y= IFDPut_125$OptionP, type="l",col="blue")
lines(x=priceRange, y= CNFDPut_125$OptionP, type="l",col="yellow")
legend("topright", c("EFD","IFD","CNFD"), col=color1, lwd=5,cex=0.5)

```

Based on the data, the American Call and put price are very similar for all the three methods. And Values become less accurate as the ds increases. On the last graph when ds =1.25 the curve is not as smooth as when ds=0.25 and 1